Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-14 analysis/paper/paper.Rmd
Split experiments in M&M and Results
It's more clear if one experiment is discussed at a time

Split up discussion

Add placeholder and reminder for a table for N treatements

## Crop Establishment {-}

Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons. For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment.

### 2015 Crop Establishment

In 2015 trays of NSIC Rc222, a short-season in-bred irrigated lowland rice variety with 114 day maturity when transplanted were established on 27 December 2014. Trays were randomised and transplanted using a mechanical transplanter.

### 2016 Crop Establishment

@@

## Inoculum {-}

## Experimental Design {-}

Both experiments consisted of split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment. The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment. The changes between seasons and experiments are detailed following.

### 2015 Dry Season Experiment {-}

The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m). Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub-plot for a whole experiment size of 1,152 sq m.

The sub-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).

### 2016 Dry Season Experiment {-}

In 2016 dry season the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment. The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m). The sub-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m). The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m). A buffer 0.5m per sub-plot was used and the overall experiment size was 3471.6 sq m.

Sub-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.

@@

## Tiller Sheath Blight Incidence {-}

@@

@@

## Tiller Sheath Blight Severity {-}

@@

## Leaf Sheath Blight Severity {-}

@@

>>>>

Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons. For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment. Details were as follows.

## 2015 Experiment {-}

### Experimental Design {-}

The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot treatment. The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment.

The main plot size was 12m x 12m (144 sq m), with a split-plot size of 5m x 5m (25 sq m). Replication size was 12m x 24m (288 sq m) with a buffer of 1m per split-plot for a whole experiment size of 1,152 sq m.

The split-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).

### Crop Establishment {-}

Trays of NSIC Rc222, a short-season inbred irrigated lowland rice variety with 114 day maturity when transplanted were established on 19 December 2014. Trays were randomised and transplanted using a mechanical transplanter on 9 January 2015.

### Inoculum Preparation and Application {-}

## 2016 Experiment {-}

### Experimental Design {-}

The experiment followed the same split-plot design as described for the 2015 experiment. However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment. The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m). The split-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m). The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m). A buffer 0.5m per split-plot was used and the overall experiment size was 3471.6 sq m.

split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.

### Crop Establishment {-}

@@

### Inoculum Preparation and Application {-}

@@

## 2015 Experiment

### Tiller Sheath Blight Incidence {-}

@@

### Tiller Sheath Blight Severity {-}

### Leaf Sheath Blight Severity {-}

## 2016 Experiment {-}

### Tiller Sheath Blight Incidence {-}

@@

### Tiller Sheath Blight Severity {-}

@@

### Leaf Sheath Blight Severity {-}

@@

# Tables {-}

Table of N application timings and dates here...
